Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-05-23 paper.tex
Some writing

[TODO: Others]

@@

@@

@@

[Tapdance]

@@

[TODO: Mention stego]

\subsubsection{Domain fronting}

@@

@@

\subsection{Tunneling and realistic behavior}

\subsubsection{Raven}

>>>>

[TODO: Others?]

@@

Snowflake took the concepts presented in Flashproxy and iterated on them and deployed them widely. Snowflake switched the transport in use from Websockets to WebRTC.\footnote{WebRTC is a commonly used standard across a variety of digital applications. Notably, it is supported in the web browser via Javascript. WebRTC is used for a variety of tasks, including video, audio, and other data, and is used by most video/audio chatting applications.} WebRTC was designed for P2P usage, and an ecosystem of utility protocols and standards has arisen around it, including tools to do NAT puncturing and establishing connections between users in various, differing networks, which provides significant utility to Snowflake compared to Websockets.\footnote{Snowflake uses Interactive Connectivity Establishment (ICE) to connect users behind NATs. ICE uses STUN and TURN relays as tools to ensure a connection can be established. STUN is commonly used and is available widely on the web, and is required for innocuous services to function as well. TURN services are less common, as they require significantly more infrastructure and are not generally permissionless like STUN.\cite{snowflake-tech}} Snowflake iterated on the rendezvous by creating a broker. The broker is reached by using a high-reliability, low-bandwidth channel (domain fronting in practice, see Section \ref{domain fronting} for further details). The broker is able to match volunteers and users to each other, in order to provide service. Snowflake then makes several usability improvements, setting up usage such that a client can fail over to a backup volunteer should their primary one fail, as well as maintaining a session across numerous volunteers using Turbotunnel.\footnote{Turbotunnel is a concept most completely implemented in Snowflake. It is a session/reliability layer that exists above an obfuscation layer.\cite{turbotunnel} Many transports exist above a reliability layer (e.g. obfs4 uses TCP), so adding an additional reliablilty layer adds notable overhead. In some cases, such as Snowflake, where the transports used are very unreliable, the benefits outweigh the costs. Turbotunnel also addresses several other issues - for example, a censor could close any long-running connections to disable obfs4.\cite{turbotunnel} Without any internal reliability layer, the connection must restart from scratch, effectively preventing usage of the transport, even if an adversary did not identify a specific bridge.}

@@

[TODO: Tapdance] [TODO: Cirripede] [TODO: Telex]

@@

@@

Most of the previously mentioned channels require either a shared secret (e.g. obfs4) or a rendezvous (e.g. snowflake). Distributing a secret or setting up a rendezvous cannot be punted indefinitely, and as such there must be a way to perform these actions, even in a censored region. High-reliability channels may be used for these actions. Though all high-reliability channels vary in numerous ways, they can generally be characterized as low-bandwidth, highly available, and sticky addresses. Each of these characteristics is important for differing reasons. Most of these channels are considered low-bandwidth - were they not, we could simply use the channel as the primary transport.\footnote{And, this can still be done, see section \ref{meek} for some discussion of using one for a full connection.} A channel must be highly available, or it could not be relied upon. Finally, sticky addresses (e.g. an email address, a social media handle) are important, as a more temporary address would leave us punting on distributing a secret or setting up a rendezvous channel - a sticky address allows one (or several) addresses to be hard-coded in a transports default config for the long run, allowing for usage without acquiring more info out-of-band.

\subsubsection{Domain fronting}
\label{domain fronting}

@@

[Raven] [Sweet]

@@

\subsubsection{Steganography}

\subsubsection{Realistic behavior}
